### 2023-06-16 resilience-safe-down.tex
up

 In this case, our contribution consist in the following:

@@

Without the additional hypothesis that
for all downward-closed set $D \subseteq S$, the set $\pred^*(D)$ is downward-closed, the problem becomes undecidable. Indeed, it is 
undecidable for Reset 
%Petri-nets
VAS whether zero (the vector containing only zeroes, also denoted~$ \textbf{0}$) is a home-state, where it is a particular case of resilience with $\Safe = \downarrow \textbf{0}$, $\Bad$ complement of $\Safe$. This stems from the fact that it is undecidable for Minsky machines with more than one counter, whether zero is a home-state. See Appendix~\ref{HS-Minsk} for a more detailed construction.

>>>>

 In the case $\Safe=\downarrow \Safe$, our contribution consist in the following:

@@

Without the additional hypothesis that
for all downward-closed set $D \subseteq S$, the set $\pred^*(D)$ is downward-closed, the problem becomes undecidable. Indeed, it is 
undecidable for Reset 
%Petri-nets
VAS whether zero (the vector containing only zeroes, also denoted~$ \textbf{0}$) is a home-state for $\N^d \setminus \textbf{0}$, where it is a particular case of resilience with $\Safe = \downarrow \textbf{0}$, $\Bad$ complement of $\Safe$. This stems from the fact that it is undecidable for Minsky machines with more than one counter, whether zero is a home-state. See Appendix~\ref{HS-Minsk} for a more detailed construction.
